---
title: "Germany Data Visualization"
author: "Taketo Muroya"
date: "2020/2/12"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(geosphere)
library(ggplot2)
library(plotly)
library(dplyr)
library(ggthemes)
library(RColorBrewer) 
library(sp)
library(maptools)
library(maps)
library(data.table)
library(choroplethr)
library(choroplethrAdmin1)
```

## Loading data

```{r}
# Germany hate crime data
devtools::install_github("davben/arvig")
library(arvig)
data("arvig")
arvig = as.data.frame(arvig)

# Germany map
germany_shape_files = readShapePoly(
  "Germany/VG250_1Jan2011_WGS84/VG250_Bundeslaender.shp")

# Crime Category and Sate
unique(arvig$category_en)
unique(arvig$state)
```

#### Comment: This data has 9 crime categories and 16 states.

***

## Data manipulation

```{r}
# Add monthly and annual variable
a <- mutate(arvig, ym = format(date, '%Y-%m'))
b <- mutate(arvig, y = format(date, '%Y'))

# Aggregate to time, category and state level
d1 = aggregate(a$ym, by=list(a$ym, a$category_en, a$state), FUN=length)
colnames(d1) = c("ym", "category", "state", "number")

# Aggregate to time and category level
d2 = aggregate(a$ym, by=list(a$ym, a$category_en), FUN=length)
colnames(d2) = c("ym", "category", "number")
d2$rate = 0
for (i in 2:nrow(d2)){
 d2$rate[i] = 100*(d2$number[i] - d2$number[i-1])/d2$number[i-1]
}
for (i in c(44,46,93,135,180,188,196)){
 d2$rate[i] = 0
}
d2 <- d2[c(-44,-45,-133,-134,-180:-187),]

# Aggregate to time level
d3 = aggregate(a$ym, by=list(a$ym), FUN=length)
colnames(d3) = c("ym", "number")
d3$rate = 0
for (i in 2:nrow(d3)){
 d3$rate[i] = 100*(d3$number[i] - d3$number[i-1])/d3$number[i-1]
}

# Aggregate to state and category level
d4 = aggregate(d1$number, by=list(d1$category, d1$state), FUN=sum)
colnames(d4) = c("category", "state", "number")
d4 <- d4[c(-11,-18,-22,-25,-27,-54,-61,-77,-84,-93),]

# Aggregate to time and state level
d5 = aggregate(b$y, by=list(b$y, b$state), FUN=length)
colnames(d5) = c("year", "state", "number")
d5$rate = 0
for (i in 2:nrow(d5)){
 d5$rate[i] = 100*(d5$number[i] - d5$number[i-1])/d5$number[i-1]
}
for (i in c(5,9,13,17,20,24,28,32,36,40,44,48,52,56,60)){
 d5$rate[i] = 0
}

# Aggregate to month and state level
d6 = aggregate(a$ym, by=list(a$ym, a$state), FUN=length)
colnames(d6) = c("ym", "state", "number")
d6$rate = 0
for (i in 2:nrow(d6)){
 d6$rate[i] = 100*(d6$number[i] - d6$number[i-1])/d6$number[i-1]
}
for (i in c(46,92,135,179,191,222,257,301,336,380,417,485,525,558)){
 d6$rate[i] = 0
}

# Aggregate to state level
d7 = aggregate(a$date, by=list(a$state), FUN=length)
colnames(d7) = c("state", "number")
others <- read.csv('others.csv')
d7 <- cbind(d7, others)
d7 <- d7[,-3]
d7$crime_pc <- 1000 * d7$number / d7$population

# Aggregate to monthly state level
d8 = aggregate(a$date, by=list(a$ym, a$state), FUN=length)
colnames(d8) = c("ym", "state", "number")

# Aggregate to time, category and state level
d9 = aggregate(arvig$date, by=list(arvig$date, arvig$state), FUN=length)
colnames(d9) = c("date", "state", "number")
```

***

## Total crime graphs

```{r}
# Total
total1 <- ggplot(d3) + 
  geom_bar(aes(x=ym, y=rate), fill="blue", 
           stat="identity", position="identity", alpha=0.5) + 
  geom_point(aes(x=ym, y=number),
            stat="identity", position="identity", colour="blue") +
  theme(legend.position = "top") + 
  labs(x="Time", y="Number of Crimes") + ggtitle("Total crimes") + 
  theme_hc() + theme(axis.text.x = element_text(angle=90, hjust=1))
total1
```

#### Comment: The trend totally changed before and after Jan-2016.

***

```{r, fig.width=10, fig.height=10}
total2 <- ggplot(d2, aes(x = ym, y = number)) + 
  geom_line(aes(group=category, color=category), size=2) +
  theme(legend.position = "top") +
  labs(x="Time", y="Number of Crimes") + 
  ggtitle("Crimes by category") +
  theme_hc() + theme(axis.text.x = element_text(angle=90, hjust=1))
total2
```

#### Comment: Most of data are from 'Miscellaneous Attack' category.

***

```{r}
total2.5 <- ggplot() +
  geom_path(data = germany_shape_files, 
            aes(x = long, y = lat, group = group)) +
  stat_density2d(
    aes(x=longitude, y=latitude, fill = ..level.., alpha = 0.25),
    size = 0.01, bins = 30, data = b, geom = "polygon") + 
  ggtitle("Total crimes: 2014-2017")
total2.5

total3 <- ggplot() +
  geom_path(data = germany_shape_files, 
            aes(x = long, y = lat, group = group)) +
  stat_density2d(
    aes(x=longitude, y=latitude, fill = ..level.., alpha = 0.25),
    size = 0.01, bins = 30, data = subset(b, y <= 2015), 
    geom = "polygon") + ggtitle("Total crimes: 2014 & 2015")
total3

total4 <- ggplot() +
  geom_path(data = germany_shape_files, 
            aes(x = long, y = lat, group = group)) +
  stat_density2d(
    aes(x=longitude, y=latitude, fill = ..level.., alpha = 0.25),
    size = 0.01, bins = 30, data = subset(b, y >= 2016), 
    geom = "polygon") + ggtitle("Total crimes: 2016 & 2017")
total4
```

#### Comment: I divided heat mapping before and after Jan-2016. The crime may expand to broader area after Jan-2016. We can change the time period according to remarkable events.

***

```{r}
state_trans <- read.csv('state_trans.csv')
d5$region <- state_trans$region

all = aggregate(d5$number, by=list(d5$region), FUN=sum)
colnames(all) = c("region", "number")
totalall <- data.frame(region=all$region, value=all$number)
total4.5 <- 
  admin1_choropleth(country.name = "germany", df = totalall, 
                    title="Total Number of Crimes by State",
                    legend = "Number", num_colors = 5)
total4.5

total2014 <- data.frame(region=subset(d5, year==2014)[,5],
                        value=subset(d5, year==2014)[,3])
total5 <- 
  admin1_choropleth(country.name = "germany", df = total2014, 
                    title="Total Number of Crimes by State (2014)",
                    legend = "Number", num_colors = 5)
total5

total2015 <- data.frame(region=subset(d5, year==2015)[,5],
                        value=subset(d5, year==2015)[,3])
total6 <- 
  admin1_choropleth(country.name = "germany", df = total2015,
                    title="Total Number of Crimes by State (2015)",
                    legend = "Number", num_colors = 5)
total6

total2016 <- data.frame(region=subset(d5, year==2016)[,5],
                        value=subset(d5, year==2016)[,3])
total7 <- 
  admin1_choropleth(country.name = "germany", df = total2016,
                    title="Total Number of Crimes by State (2016)",
                    legend = "Number", num_colors = 5)
total7

total2017 <- data.frame(region=subset(d5, year==2017)[,5],
                        value=subset(d5, year==2017)[,3])
total8 <- 
  admin1_choropleth(country.name = "germany", df = total2017,
                    title="Total Number of Crimes by State (2017)",
                    legend = "Number", num_colors = 5)
total8

total2015r <- data.frame(region=subset(d5, year==2015)[,5],
                        value=subset(d5, year==2015)[,4])
total9 <- 
  admin1_choropleth(country.name = "germany", df = total2015r,
                    title="Total Change of Crimes by State (2015)",
                    legend = "% Change", num_colors = 5)
total9

total2016r <- data.frame(region=subset(d5, year==2016)[,5],
                        value=subset(d5, year==2016)[,4])
total10 <- 
  admin1_choropleth(country.name = "germany", df = total2016r,
                    title="Total Change of Crimes by State (2016)",
                    legend = "% Change", num_colors = 5)
total10

total2017r <- data.frame(region=subset(d5, year==2017)[,5],
                        value=subset(d5, year==2017)[,4])
total11 <- 
  admin1_choropleth(country.name = "germany", df = total2017r,
                    title="Total Change of Crimes by State (2017)",
                    legend = "% Change", num_colors = 5)
total11
```

***

```{r, fig.width=10, fig.height=10}
total12 <- ggplot(d4) + 
  geom_bar(aes(x=state, y=number, group=category, fill=category), 
           stat="identity") + theme(legend.position = "top") +
  labs(x="State", y="Number of Crimes") + 
  ggtitle("Crimes by State") + 
  theme_hc() + theme(axis.text.x = element_text(angle=90, hjust=1))
total12
```

***

## Crime per capita graphs

```{r}
state_trans <- read.csv('state_trans2.csv')
d7$region <- state_trans$region

crime_per_capita <- data.frame(region=d7[,7], value=d7[,6])
total13 <- 
  admin1_choropleth(country.name = "germany", df = crime_per_capita,
                    title="Refugee Crimes per population by State",
                    legend = "crime / population(million)", 
                    num_colors = 5)
total13

poverty <- data.frame(region=d7[,7], value=d7[,4])
total14 <- 
  admin1_choropleth(country.name = "germany", df = poverty,
                    title="Poverty level by State", 
                    legend = "poverty level (%)", 
                    num_colors = 5)
total14

AFD <- data.frame(region=d7[,7], value=d7[,5])
total15 <- 
  admin1_choropleth(country.name = "germany", df = AFD,
                    title="AFD vote by State", 
                    legend = "AFD vote (%)", 
                    num_colors = 5)
total15

result <- lm(crime_pc ~ poverty + AFD, data=d7)
summary(result)

total16 <- ggplot(data = d7, aes(x = crime_pc, y = poverty)) +
  geom_point()+
  xlab("Refugee Crimes per population") + ylab("Poverty level") + 
  theme_economist() + theme(legend.position="none") + 
  ggtitle("Rrefugee crime and poverty level")
total16

total17 <- ggplot(data = d7, aes(x = crime_pc, y = AFD)) +
  geom_point()+geom_smooth(color="blue", lwd=1, se=FALSE, method=lm)+ 
  xlab("Refugee Crimes per population") + ylab("AFD vote rate") + 
  theme_economist() + theme(legend.position="none") + 
  ggtitle("Rrefugee crime and AFD vote")
total17
```

***

## 1. December 2015 VS January 2016

```{r}
data201511 = subset(d8, ym=="2015-11")
others <- read.csv('others.csv')
others <- others[-5,]
others <- others[-11,]
data201511 <- cbind(data201511, others)
data201511 <- data201511[,-4]
data201511$crime_pc <- 1000 * data201511$number / data201511$population
state_trans <- read.csv('state_trans2.csv')
state_trans <- state_trans[-5,]
state_trans <- state_trans[-11,]
data201511$region <- state_trans$region

data201512 = subset(d8, ym=="2015-12")
others <- read.csv('others.csv')
others <- others[-5,]
data201512 <- cbind(data201512, others)
data201512 <- data201512[,-4]
data201512$crime_pc <- 1000 * data201512$number / data201512$population
state_trans <- read.csv('state_trans2.csv')
state_trans <- state_trans[-5,]
data201512$region <- state_trans$region

data201601 = subset(d8, ym=="2016-01")
others <- read.csv('others.csv')
data201601 <- cbind(data201601, others)
data201601 <- data201601[,-4]
data201601$crime_pc <- 1000 * data201601$number / data201601$population
state_trans <- read.csv('state_trans2.csv')
data201601$region <- state_trans$region

mix1 <- rbind(data201511, data201512, data201601)
mix1 <- mix1[order(mix1$state),]
mix1$rate = 0
for (i in 2:nrow(mix1)){
 mix1$rate[i] = 
   100*(mix1$crime_pc[i] - mix1$crime_pc[i-1])/mix1$crime_pc[i-1]
}

crime201512 <- data.frame(
  region=subset(mix1, ym=="2015-12")[,8], 
  value=subset(mix1, ym=="2015-12")[,7])
total18 <- 
  admin1_choropleth(country.name = "germany", df = crime201512,
                    title="Crimes per population by State (Dec.2015)",
                    legend = "crime / population(million)", 
                    num_colors = 5)
total18

crime201601 <- data.frame(
  region=subset(mix1, ym=="2016-01")[,8], 
  value=subset(mix1, ym=="2016-01")[,7])
total19 <- 
  admin1_choropleth(country.name = "germany", df = crime201601,
                    title="Crimes per population by State (Jan.2016)",
                    legend = "crime / population(million)", 
                    num_colors = 5)
total19

rate201512 <- data.frame(
  region=subset(mix1, ym=="2015-12")[,8], 
  value=subset(mix1, ym=="2015-12")[,9])
total20 <- 
  admin1_choropleth(country.name = "germany", df = rate201512,
                    title="Crimes per population growth by State (Dec.2015)",
                    legend = "crime per population growth (%)", 
                    num_colors = 5)
total20

rate201601 <- data.frame(
  region=subset(mix1, ym=="2016-01")[,8], 
  value=subset(mix1, ym=="2016-01")[,9])
total21 <- 
  admin1_choropleth(country.name = "germany", df = rate201601,
                    title="Crimes per population growht by State (Jan.2016)",
                    legend = "crime per population growth (%)", 
                    num_colors = 5)
total21
```

## 2. July 5, 2016 - July 18th, 2016 VS Juli, 19 2016 - August 2, 2016

```{r}
aaa = subset(d9, date >= "2016-07-05")
bbb = subset(aaa, date <= "2016-07-18")
before2 = aggregate(bbb$number, by=list(bbb$state), FUN=sum)
colnames(before2) = c("state", "number")

others <- read.csv('others.csv')
others <- others[-5,]
before2 <- cbind(before2, others)
before2 <- before2[,-3]
before2$crime_pc <- 1000 * before2$number / before2$population
state_trans <- read.csv('state_trans2.csv')
state_trans <- state_trans[-5,]
before2$region <- state_trans$region

before22 <- data.frame(region=before2$region, value=before2$crime_pc)
total22 <- admin1_choropleth(country.name = "germany", df = before22, title="Crimes per population by State (Jul 5th - 18th, 2016)", legend = "crime / population(million)", num_colors = 5)
total22

ccc = subset(d9, date >= "2016-07-19")
ddd = subset(ccc, date <= "2016-08-02")
after2 = aggregate(ddd$number, by=list(ddd$state), FUN=sum)
colnames(after2) = c("state", "number")

others <- read.csv('others.csv')
others <- others[-5,]
after2 <- cbind(after2, others)
after2 <- after2[,-3]
after2$crime_pc <- 1000 * after2$number / after2$population
state_trans <- read.csv('state_trans2.csv')
state_trans <- state_trans[-5,]
after2$region <- state_trans$region

after22 <- data.frame(region=after2$region, value=after2$crime_pc)
total23 <- admin1_choropleth(country.name = "germany", df = after22, title="Crimes per population by State (Jul 19th - Aug 2nd, 2016)", legend = "crime / population(million)", num_colors = 5)
total23
```

## 3. Dec 5, 2016 - Dec 18, 2016 VS Dec, 19 2016 - Jan 2, 2017

```{r}
aaa = subset(d9, date >= "2016-12-05")
bbb = subset(aaa, date <= "2016-12-18")
before2 = aggregate(bbb$number, by=list(bbb$state), FUN=sum)
colnames(before2) = c("state", "number")

others <- read.csv('others.csv')
others <- others[-5,]
others <- others[-5,]
others <- others[-9,]
others <- others[-9,]
before2 <- cbind(before2, others)
before2 <- before2[,-3]
before2$crime_pc <- 1000 * before2$number / before2$population
state_trans <- read.csv('state_trans2.csv')
state_trans <- state_trans[-5,]
state_trans <- state_trans[-5,]
state_trans <- state_trans[-9,]
state_trans <- state_trans[-9,]
before2$region <- state_trans$region

before22 <- data.frame(region=before2$region, value=before2$crime_pc)
total24 <- admin1_choropleth(country.name = "germany", df = before22, title="Crimes per population by State (Dec 5th - 18th, 2016)", legend = "crime / population(million)", num_colors = 5)
total24

ccc = subset(d9, date >= "2016-12-19")
ddd = subset(ccc, date <= "2017-01-02")
after2 = aggregate(ddd$number, by=list(ddd$state), FUN=sum)
colnames(after2) = c("state", "number")

others <- read.csv('others.csv')
others <- others[-5,]
others <- others[-5,]
others <- others[-10,]
after2 <- cbind(after2, others)
after2 <- after2[,-3]
after2$crime_pc <- 1000 * after2$number / after2$population
state_trans <- read.csv('state_trans2.csv')
state_trans <- state_trans[-5,]
state_trans <- state_trans[-5,]
state_trans <- state_trans[-10,]
after2$region <- state_trans$region

after22 <- data.frame(region=after2$region, value=after2$crime_pc)
total25 <- admin1_choropleth(country.name = "germany", df = after22, title="Crimes per population by State (Dec 19th, 2016 - Jan 2nd, 2017)", legend = "crime / population(million)", num_colors = 5)
total25
```

***

```{r, include=FALSE}
png("image/total1.png", width = 600, height = 450)
total1
dev.off()
png("image/total2.png", width = 600, height = 450)
total2
dev.off()
png("image/total2-5.png", width = 600, height = 450)
total2.5
dev.off()
png("image/total3.png", width = 600, height = 450)
total3
dev.off()
png("image/total4.png", width = 600, height = 450)
total4
dev.off()
png("image/total4-5.png", width = 600, height = 450)
total4.5
dev.off()
png("image/total5.png", width = 600, height = 450)
total5
dev.off()
png("image/total6.png", width = 600, height = 450)
total6
dev.off()
png("image/total7.png", width = 600, height = 450)
total7
dev.off()
png("image/total8.png", width = 600, height = 450)
total8
dev.off()
png("image/total9.png", width = 600, height = 450)
total9
dev.off()
png("image/total10.png", width = 600, height = 450)
total10
dev.off()
png("image/total11.png", width = 600, height = 450)
total11
dev.off()
png("image/total12.png", width = 600, height = 450)
total12
dev.off()
png("image/total13.png", width = 600, height = 450)
total13
dev.off()
png("image/total14.png", width = 600, height = 450)
total14
dev.off()
png("image/total15.png", width = 600, height = 450)
total15
dev.off()
png("image/total16.png", width = 600, height = 450)
total16
dev.off()
png("image/total17.png", width = 600, height = 450)
total17
dev.off()
png("image/total18.png", width = 600, height = 450)
total18
dev.off()
png("image/total19.png", width = 600, height = 450)
total19
dev.off()
png("image/total20.png", width = 600, height = 450)
total20
dev.off()
png("image/total21.png", width = 600, height = 450)
total21
dev.off()
png("image/total22.png", width = 600, height = 450)
total22
dev.off()
png("image/total23.png", width = 600, height = 450)
total23
dev.off()
png("image/total24.png", width = 600, height = 450)
total24
dev.off()
png("image/total25.png", width = 600, height = 450)
total25
dev.off()
```

***

## Arson graphs

```{r}
# Arson
arson1 <- ggplot(subset(d2, category=='arson'), 
                aes(x = ym, y = number)) + 
  geom_point() + theme(legend.position = "top") +
  labs(x="Time", y="Number of Crimes") + ggtitle("Arson") +
  theme_hc() + theme(axis.text.x = element_text(angle=90, hjust=1))
arson1

arson <- subset(b, category_en=='arson')

arson2 <- ggplot() +
  geom_path(data = germany_shape_files, 
            aes(x = long, y = lat, group = group)) +
  stat_density2d(
    aes(x=longitude, y=latitude, fill = ..level.., alpha = 0.25),
    size = 0.01, bins = 30, data = subset(arson, y <= 2015), 
    geom = "polygon") + ggtitle("Arson: 2014 & 2015")
arson2

arson3 <- ggplot() +
  geom_path(data = germany_shape_files, 
            aes(x = long, y = lat, group = group)) +
  stat_density2d(
    aes(x=longitude, y=latitude, fill = ..level.., alpha = 0.25),
    size = 0.01, bins = 30, data = subset(arson, y >= 2016), 
    geom = "polygon") + ggtitle("Arson: 2016 & 2017")
arson3
```

```{r, include=FALSE}
png("image/arson1.png", width = 600, height = 450)
arson1
dev.off()
png("image/arson2.png", width = 600, height = 450)
arson2
dev.off()
png("image/arson3.png", width = 600, height = 450)
arson3
dev.off()
```

***

## Assault graphs

```{r}
# Assault
assault1 <- ggplot(subset(d2, category=='assault'), 
                aes(x = ym, y = number)) + 
  geom_point() + theme(legend.position = "top") +
  labs(x="Time", y="Number of Crimes") + ggtitle("Assault") +
  theme_hc() + theme(axis.text.x = element_text(angle=90, hjust=1))
assault1

assault <- subset(b, category_en=='assault')

assault2 <- ggplot() +
  geom_path(data = germany_shape_files, 
            aes(x = long, y = lat, group = group)) +
  stat_density2d(
    aes(x=longitude, y=latitude, fill = ..level.., alpha = 0.25),
    size = 0.01, bins = 30, data = subset(assault, y <= 2015), 
    geom = "polygon") + ggtitle("Assault: 2014 & 2015")
assault2

assault3 <- ggplot() +
  geom_path(data = germany_shape_files, 
            aes(x = long, y = lat, group = group)) +
  stat_density2d(
    aes(x=longitude, y=latitude, fill = ..level.., alpha = 0.25),
    size = 0.01, bins = 30, data = subset(assault, y >= 2016), 
    geom = "polygon") + ggtitle("Assault: 2016 & 2017")
assault3
```

```{r, include=FALSE}
png("image/assault1.png", width = 600, height = 450)
assault1
dev.off()
png("image/assault2.png", width = 600, height = 450)
assault2
dev.off()
png("image/assault3.png", width = 600, height = 450)
assault3
dev.off()
```

***

## Demonstration graphs

```{r}
# Demonstration
demo1 <- ggplot(subset(d2, category=='demonstration'), 
                aes(x = ym, y = number)) + 
  geom_point() + theme(legend.position = "top") +
  labs(x="Time", y="Number of Crimes") + ggtitle("Demonstration") +
  theme_hc() + theme(axis.text.x = element_text(angle=90, hjust=1))
demo1

demo <- subset(b, category_en=='demonstration')

demo2 <- ggplot() +
  geom_path(data = germany_shape_files, 
            aes(x = long, y = lat, group = group)) +
  stat_density2d(
    aes(x=longitude, y=latitude, fill = ..level.., alpha = 0.25),
    size = 0.01, bins = 30, data = subset(demo, y <= 2015), 
    geom = "polygon") + ggtitle("Demonstration: 2014 & 2015")
demo2

demo3 <- ggplot() +
  geom_path(data = germany_shape_files, 
            aes(x = long, y = lat, group = group)) +
  stat_density2d(
    aes(x=longitude, y=latitude, fill = ..level.., alpha = 0.25),
    size = 0.01, bins = 30, data = subset(demo, y >= 2016), 
    geom = "polygon") + ggtitle("Demonstration: 2016 & 2017")
demo3
```

```{r, include=FALSE}
png("image/demo1.png", width = 600, height = 450)
demo1
dev.off()
png("image/demo2.png", width = 600, height = 450)
demo2
dev.off()
png("image/demo3.png", width = 600, height = 450)
demo3
dev.off()
```

***

## Miscellaneous Attack graphs

```{r}
# Miscellaneous Attack
att1 <- ggplot(subset(d2, category=='miscellaneous attack'), 
                aes(x = ym, y = number)) + 
  geom_point() + theme(legend.position = "top") +
  labs(x="Time", y="Number of Crimes") + 
  ggtitle("Miscellaneous Attack") +
  theme_hc() + theme(axis.text.x = element_text(angle=90, hjust=1))
att1

att <- subset(b, category_en=='miscellaneous attack')

att2 <- ggplot() +
  geom_path(data = germany_shape_files, 
            aes(x = long, y = lat, group = group)) +
  stat_density2d(
    aes(x=longitude, y=latitude, fill = ..level.., alpha = 0.25),
    size = 0.01, bins = 30, data = subset(att, y <= 2015), 
    geom = "polygon") + 
  ggtitle("Miscellaneous Attack: 2014 & 2015")
att2

att3 <- ggplot() +
  geom_path(data = germany_shape_files, 
            aes(x = long, y = lat, group = group)) +
  stat_density2d(
    aes(x=longitude, y=latitude, fill = ..level.., alpha = 0.25),
    size = 0.01, bins = 30, data = subset(demo, y >= 2016), 
    geom = "polygon") + 
  ggtitle("Miscellaneous Attack: 2016 & 2017")
att3
```

```{r, include=FALSE}
png("image/att1.png", width = 600, height = 450)
att1
dev.off()
png("image/att2.png", width = 600, height = 450)
att2
dev.off()
png("image/att3.png", width = 600, height = 450)
att3
dev.off()
```

#### Comment: For Miscellaneous Attack, the crime area may shrink after Jan-2016.

***

## Suspicion graphs

```{r}
# Suspicion
ggplot(subset(d2, category=='suspicion'), 
                aes(x = ym, y = number)) + 
  geom_point() + theme(legend.position = "top") +
  labs(x="Time", y="Number of Crimes") + ggtitle("Suspicion") +
  theme_hc() + theme(axis.text.x = element_text(angle=90, hjust=1))

sus <- subset(b, category_en=='suspicion')

ggplot() +
  geom_path(data = germany_shape_files, 
            aes(x = long, y = lat, group = group)) +
  stat_density2d(
    aes(x=longitude, y=latitude, fill = ..level.., alpha = 0.25),
    size = 0.01, bins = 30, data = subset(sus, y >= 2016), 
    geom = "polygon") + ggtitle("Suspicion: 2016 & 2017")
```

***

## Other graphs

```{r}
# Other
ggplot(subset(d2, category=='other'), 
                aes(x = ym, y = number)) + 
  geom_point() + theme(legend.position = "top") +
  labs(x="Time", y="Number of Crimes") + ggtitle("Other") +
  theme_hc() + theme(axis.text.x = element_text(angle=90, hjust=1))

other <- subset(b, category_en=='other')

ggplot() +
  geom_path(data = germany_shape_files, 
            aes(x = long, y = lat, group = group)) +
  stat_density2d(
    aes(x=longitude, y=latitude, fill = ..level.., alpha = 0.25),
    size = 0.01, bins = 30, data = subset(other, y <= 2015), 
    geom = "polygon") + ggtitle("Other: 2014 & 2015")
```

***

## Refugee graphs

```{r}
refugee <- read.csv('refugee.csv')
r <- subset(
  refugee, year == 2014 | year == 2015 | year == 2016 | year == 2017)
ref <- aggregate(r$number, by=list(r$ym), FUN=sum)
colnames(ref) = c("ym", "number")
```

```{r}
ref1 <- ggplot(data = ref, aes(x = ym, y = number)) +
  geom_point() + geom_smooth(color="blue", lwd=1, se=FALSE) + 
  xlab("time") + ylab("Refugee influx") + 
  theme_economist() + theme(legend.position="none") + 
  ggtitle("Refugee Influx over time") + 
  theme(axis.text.x = element_text(angle=90, hjust=1))
ref1
```

#### Comment: Refugee number in Germany looks strongly correlated with crime data. Although I could not find state level data for refugee data, we may analyze something related to refugee data.

```{r}
refugee <- read.csv('refugee.csv')
ref <- aggregate(refugee$number, by=list(refugee$ym), FUN=sum)
colnames(ref) = c("ym", "number")
```

```{r}
ref2 <- ggplot(data = ref, aes(x = ym, y = number)) +
  geom_point() + geom_smooth(color="blue", lwd=1, se=FALSE) + 
  xlab("time") + ylab("Refugee influx") + 
  theme_economist() + theme(legend.position="none") + 
  ggtitle("Refugee Influx over time") + 
  theme(axis.text.x = element_text(angle=90, hjust=1))
ref2
```

#### http://popstats.unhcr.org/en/asylum_seekers_monthly

```{r}
refstate <- read.csv('refugee_state.csv')
colnames(refstate) = c("State","Y2016","Y2017","Y2018","Y2019")
refstate$total <- refstate$Y2016 + refstate$Y2017 + 
                  refstate$Y2018 + refstate$Y2019
```

```{r, fig.width=10, fig.height=10}
ref3 <- ggplot(refstate) + 
  geom_bar(aes(x=State, y=total), stat="identity", fill='blue') + 
  theme(legend.position = "top") + 
  ggtitle("Refugees by state (2016-2019)") + 
  labs(x="State", y="Number of Refugees") + 
  theme_hc() + theme(axis.text.x = element_text(angle=90, hjust=1))
ref3

ref4 <- ggplot(refstate) + 
  geom_bar(aes(x=State, y=Y2016), stat="identity", fill='blue') + 
  theme(legend.position = "top") + 
  ggtitle("Refugees by state (2016)") + 
  labs(x="State", y="Number of Refugees") + 
  theme_hc() + theme(axis.text.x = element_text(angle=90, hjust=1))
ref4

ref5 <- ggplot(refstate) + 
  geom_bar(aes(x=State, y=Y2017), stat="identity", fill='blue') + 
  theme(legend.position = "top") + 
  ggtitle("Refugees by state (2017)") + 
  labs(x="State", y="Number of Refugees") + 
  theme_hc() + theme(axis.text.x = element_text(angle=90, hjust=1))
ref5

ref6 <- ggplot(refstate) + 
  geom_bar(aes(x=State, y=Y2018), stat="identity", fill='blue') + 
  theme(legend.position = "top") + 
  ggtitle("Refugees by state (2018)") + 
  labs(x="State", y="Number of Refugees") + 
  theme_hc() + theme(axis.text.x = element_text(angle=90, hjust=1))
ref6

ref7 <- ggplot(refstate) + 
  geom_bar(aes(x=State, y=Y2019), stat="identity", fill='blue') + 
  theme(legend.position = "top") + 
  ggtitle("Refugees by state (2019)") + 
  labs(x="State", y="Number of Refugees") + 
  theme_hc() + theme(axis.text.x = element_text(angle=90, hjust=1))
ref7
```

## Crimes by month/asylum applications

```{r}
q <- read.csv("applicants.csv")
q$crime <- 0
for (i in 1:22){
 q$crime[i] = d3$number[3*(i-1)+1]+d3$number[3*(i-1)+2]+d3$number[3*(i-1)+3]
}

ref8 <- ggplot(data = q, aes(x = time, y = crime)) +
  geom_point() + geom_smooth(color="blue", lwd=1, se=FALSE) + 
  xlab("time") + ylab("Refugee Crimes") + 
  theme_economist() + theme(legend.position="none") + 
  ggtitle("Refugee Crimes over time") + 
  theme(axis.text.x = element_text(angle=90, hjust=1))
ref8

ref9 <- ggplot(data = q, aes(x = time, y = applicants)) +
  geom_point() + geom_smooth(color="blue", lwd=1, se=FALSE) + 
  xlab("time") + ylab("Refugee Applications") + 
  theme_economist() + theme(legend.position="none") + 
  ggtitle("Rregee Applications over time") + 
  theme(axis.text.x = element_text(angle=90, hjust=1))
ref9
```

```{r, include=FALSE}
png("image/ref1.png", width = 600, height = 450)
ref1
dev.off()
png("image/ref2.png", width = 600, height = 450)
ref2
dev.off()
png("image/ref3.png", width = 600, height = 450)
ref3
dev.off()
png("image/ref4.png", width = 600, height = 450)
ref4
dev.off()
png("image/ref5.png", width = 600, height = 450)
ref5
dev.off()
png("image/ref6.png", width = 600, height = 450)
ref6
dev.off()
png("image/ref7.png", width = 600, height = 450)
ref7
dev.off()
png("image/ref8.png", width = 600, height = 450)
ref8
dev.off()
png("image/ref9.png", width = 600, height = 450)
ref9
dev.off()
```

***

## Prediction

```{r}
library(forecast)
library(urca)
crime_ts <- ts(d3$number, start=c(2014,1), frequency=12)

# Unit Root Test
summary(ur.kpss(crime_ts))

# Autocorrelation
ggtsdisplay(crime_ts, main="Autocorrelation")

# Seasonality
ggsubseriesplot(crime_ts, main="Seasonality")

# Model Selection using only crime data
model <- auto.arima(
  y=crime_ts, ic="aic", max.order=7, 
  stepwise=F, approximation=F, parallel=T, num.cores=4 
)

# Best Model using only crime data
model

# Prediction using only crime data
prediction <- forecast(
  model, h=11, level=c(95,70)
)
prediction

autoplot(prediction, predict.colour=1, 
         main="Prediction using only crime data")

# Loading refugee data
r2 <- subset(refugee, year == 2014 | year == 2015 | 
               year == 2016 | year == 2017 | year == 2018)
reff <- aggregate(r2$number, by=list(r2$ym), FUN=sum)
colnames(reff) = c("ym", "number")

refugee_ts <- ts(reff$number, start=c(2014,1), frequency=12)
refugee_ts_train <- window(refugee_ts, end=c(2017,11))
refugee_ts_test <- window(refugee_ts, start=c(2017,12))

# Refugee data
plot(refugee_ts, main="Refugee influx data")

# Model Selection with refugee data
model <- auto.arima(
  y=crime_ts, xreg=refugee_ts_train, ic="aic", max.order=7, 
  stepwise=F, approximation=F, parallel=T, num.cores=4 
)

# Best Model with refugee data
model

# Prediction with refugee data
prediction <- forecast(
  model, xreg=refugee_ts_test, h=11, level=c(95,70)
)
prediction

autoplot(prediction, predict.colour=1, 
         main="Prediction with refugee data")
```