---
title: "DSPP Assignment 1_UK2"
author: "Evelyn"
date: "2/9/2020"
output:
  html_document:
    df_print: paged
    code_folding: hide
    toc: yes
---

# Loading and Viewing Data

```{r, warnings=FALSE, messages=FALSE}
# load packages
library(geosphere)
library(ggplot2)
library(plotly)
library(ggthemes)
library(RColorBrewer) 
library(sp)
library(maptools)
library(maps)
library(data.table)
library(tidyverse)
library(DT)
library(ggmap)
library(mapproj)
library(rgdal)
library(leaflet)
library(ggrepel)

# set working directory
setwd("C:/Users/ydeng.AIR/Desktop/Evelyn/1. Columbia/04. DSPP/Presentation 1 - Crime")

```


```{r}
# load data 
base::load("police_incidents_df.rdata")
#base::load("uk_aggregated.rdata")
#base::load("uk_aggregated_anti_social.rdata")

# view data
head(police_incidents,10)
#head(uk_aggregated,1000)              
#head(uk_aggregated_anti_social, 1000) 

```

# Analysis of Crime by Crime Type

## Data Cleaning and Restructuring

```{r}
# choose only necessary variables
crime <- police_incidents[c(2,4,5,6,10)]
crime
table(crime$Crime.type)

```

```{r}
# create dataset with aggregated crime by month by type
crime_freq_by_month <- crime %>%
  group_by(Month, Crime.type) %>%
  summarise(frequency = n())

crime_freq_by_month

```

## Visualize Data: Crime by Month and Type

```{r, fig.height=9, fig.width=12}

graph <- ggplot(crime_freq_by_month, aes(x = Month, y = frequency)) + 
  geom_line(aes(group=Crime.type, color = Crime.type)) +
  #geom_point(size = 2, shape = 21, fill = "lightblue") +
  theme(legend.position = "top") +
  labs(x="Month", y="Number of Crimes") + 
  ggtitle("Monthly Crime Frequency in the UK") +
  theme_hc() + theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplotly(graph, tooltip = c("x", "y", "group"), dynamicTicks=TRUE)


```

## Insights

ASB is the most frequent crime, followed by violent and sexual offenses

seasonal crime peaks:
  - anti-social behavior(ASB)    summer
  - violent and sexual offences  summer
  - other theft                  summer
  - bicycle theft                summer
  - public order                 summer
  - burglary                     fall to early winter
  - theft from the person        early winter (December)
  
the seasonality of crime is most notable for:
  - ASB         (approx 45%  more crime during peak season)
  - bike theft  (approx 100% more crime during peak season)


Note: Increase in crime is not a reflection of increase in population, which was only about 2% from 2014 to 2017 (office for national statistics: https://www.ons.gov.uk/peoplepopulationandcommunity/populationandmigration/populationestimates/articles/overviewoftheukpopulation/august2019)